---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ecointeraction

<!-- badges: start -->
<!-- badges: end -->

This is ecointeraction package. The main goal is provide tools to model and
potential interactions given known interactions and predict unknown interactions
based, but not limited, on phylogenetic, environmental and geographic distance 
among the host.

## Installation

You can install the development version of ecointeraction from [GitHub](https://github.com/alrobles/ecointeraction) with:

``` r
# install.packages("devtools")
devtools::install_github("alrobles/ecointeraction")
```

## Example

We explore a raw data base of mammal virus.
    
```{r example1}
library(ecointeraction)
mammalvirus
```

```{r example11, echo=FALSE}
knitr::kable(head(mammalvirus))
```
We use the function accumulate_incidence


```{r example2}
library(ecointeraction)
ecointeraction::accumulate_incidence(data = mammalvirus, group = mammal_species, incidence = incidence)
```



```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
