---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ecointeraction

<!-- badges: start -->
<!-- badges: end -->

This is ecointeraction package. The main goal is provide tools to model and
potential interactions given known interactions and predict unknown interactions
based, but not limited, on phylogenetic, environmental and geographic distance 
among the host.

## Installation

You can install the development version of ecointeraction from [GitHub](https://github.com/alrobles/ecointeraction) with:

``` r
# install.packages("devtools")
devtools::install_github("alrobles/ecointeraction")
```

## Example

We explore a raw data base of mammal virus.
    
```{r example2, echo=FALSE}
library(ecointeraction)
knitr::kable(head(mammalvirus))
```
We use the function accumulate_incidence to get how many reported cases there is 
for each host species. We use this information to create the datasets to train.

```{r example3}

mammal_flavivirus_incidence <- accumulate_incidence(data = mammalvirus,
                                                    group = mammal_species,
                                                    incidence = incidence)
```

We print here the frist 6 with head.

```{r example4, echo=FALSE}
knitr::kable(head(mammal_flavivirus_incidence))
```


We use the cutoff_incidence function to keet just the portion of host that has
more information about the system.

```{r example5}
flavivirus_host <- cutoff_incidence(mammal_flavivirus_incidence)
```

```{r example6, echo=FALSE}
knitr::kable(flavivirus_host)
```


## Prepare data for modelling
Now we can prepare the dataset for modelling using a distance table. We provide 
here a distance table calculated befare using mean distance from one target host
to the other host. We show here the full pipeline using a count table
of plasmodium reported for each host species. Then we use the
`accumulate_incidence` function and the `cuttoff_incidence` to keep the host with
the most information. Then we use  `prep_incidence_data`  to prepare the data for
modelling using the `birdsdistance` dataset we provide and print the fifteen 
first rows




```{r example7}
plasmodium_data <- birdsplasmodium %>%
     accumulate_incidence(group = species) %>%
     cutoff_incidence() %>%
     prep_incidence_data(distance  = birdsdistance) 
```
```{r example8, echo=TRUE}
models <- automodel_replication(plasmodium_data, birdsdistance)
models$roc
```

